% 
% This is the Title and Approval Page file (dissertation-tap.tex) for
% a dissertation.
%
% The order of the commands below is very important.
% You may choose to add or eliminate a \prefacesection 
% in the front material but the order should remain 
% the same especially \maketocloflot followed by 
% \prefacesectiontoc{Abstract}

% Title and author are also used for PDF file properties
% No special character or commands can be used for the PDF definition; 
% use the [options] paramater to specify a different title or author 
% to remove special characters or commands like \\ for example.
\title[First Line of Title Second Line of Title]{Emulsions Stabilized by Magnetic Ellipsoidal Particles: A Lattice Boltzmann Study}
\author{Nikhil Karthikeyan}
\type{dissertation}
\degree{Doctor of Philosophy}
\majorfieldtrue\majorfield{Materials Science and Engineering}
\degreedate{Spring 2025}
% Optional PDF properties
\keywords{Keyord,Keyword,Keyword}
\subject{Subject}

\maketitlepage % Generates Title Page

\begin{approvalpage}
\chair{Joshua Zide, Ph.D.}{Chair of the Department of Materials Science and Engineering}
\dean{Pamela M. Norris, Ph.D.}{Dean of the College of Engineering}
\end{approvalpage}

\begin{signedpage} % Up to 4 signatures
\profmember{Ulf D. Schiller, Ph.D.}
\member{Eric M. Furst, Ph.D.}
\member{Arthi Jayaraman, Ph.D.}
\member{Darrin Pochan, Ph.D.}
\end{signedpage}

% For additional signatures beyond 4, uncomment and use
% \begin{signedpagecont}
% \member{Xxxx Xxxx, Highest Degree}
% \member{Xxxx Xxxx, Highest Degree}
% \end{signedpagecont}

\begin{front} % Starts front material (Roman style page numbers)

\prefacesection{Acknowledgements}
%\input{acknowl} % This file (acknowl.tex) contains the text
                % for the acknowledgments or type text here.

In the development of this dissertation, I extend my deepest gratitude to Dr Ulf Schiller whose support, motivation and 
opportunities have been indispensible during my PhD. I believe his methodical problem solving strategies, depth and 
breadth of knowledge have been invaluable sources of inspiration for me as well as 
motivation to strive towards those ideals. I would also like to thank members of my committee, 
from the University of Delaware and Clemson University for their mentorship 
and motivation that pushed me to increase my breadth of knowledge and to think outside the box.

Listing everyone I am grateful for who have provided me non-academic support would be too long for this page. 
I am grateful to my family, with whom I may not be the best at 
discussing my future plans, but they have been an indispensible source of support during my time away from home. 
I am thankful to my lab members especially for adding brief moments of levity during my PhD and giving me the 
opportunity to be a part of their own journey in graduate school. Thank you to everyone who has been with me 
through thick and thin, and to many more celebrations of our achievements. 

% Table of Contents is always created, but you
% may set \tablespagefalse and \figurespagefalse 
% if you don't want these generated automatically
% (i.e. List of Tables and List of Figures).
% These are set to true by default (i.e. \tablespagetrue,
% \figurespagetrue).

% Uncomment if you do not want a List of Figures.
%\figurespagefalse

% Uncomment if you do not want a List of Tables.
%\tablespagefalse 

\maketocloflot

\prefacesectiontoc{Abstract}
%\input{abstract} % This file (abstract.tex) contains the text
                 % for an abstract or type text here.
    Porous materials are important across a wide range of applications, including water filtration, catalyst supports, 
    battery electrodes, and bioengineered materials. To accommodate a broader range of pore sizes and enable scalable 
    fabrication with minimal waste, bottom-up synthesis techniques have gained increasing attention. Emulsion templating 
    leverages thermodynamic or kinetically arrested structures formed by phase-separating fluids. Among these, bicontinuous 
    interfacially jammed emulsion gels (bijels) are particularly interesting due to their tortuous and co-continuous microstructures.

    Bijels were first formed via thermally induced spinodal decomposition of partially miscible fluid mixtures in the presence of neutrally 
    wetting particles. As the fluid domains coarsen, particles adsorb onto the interface until the interfacial area matches the 
    total cross-sectional area of the particles, resulting in a jammed monolayer that locks the microstructure in place. Traditional 
    bijel synthesis via thermal phase separation is not readily scalable as the cooling rate cannot be uniformly controlled, which
    reduces uniformity of the structure. However, newer techniques such as Solvent Transfer Induced Phase Separation (STrIPS) have been 
    developed to address the scale up limitation/ utilizing the removal of solvent from a bijel casting
    mixture to induce phase separation. STrIPS allows for the decoupling of spinodal decomposition from temperature, allowing for greater
    material compatibility and tunable bijel shapes and microstructure through controlling the solvent exchange rate. However, the 
    microstructure obtained is coupled to the casting mixture composition, and the flow rate during STrIPS.
    
    One promising approach to modulate bijel microstructure is through stimulus-responsive systems. Magnetic stimuli, in particular, 
    offer a controllable and targeted mechanism. Earlier studies using spherical particles under magnetic fields showed 
    limited microstructural changes. However, ellipsoidal particles can respond to magnetic actuation 
    by tilting, leading to the multipolar capillary interactions between particles facilitating formation of particle chains or rings at 
    interfaces. This phenomenon opens the door to controllable modifications in bijel microstructures using magnetic fields.
    
    This dissertation investigates whether constant magnetic fields can be used to control the microstructure of bijels stabilized by 
    magnetically responsive ellipsoidal particles. To explore this, we employ a multicomponent Lattice Boltzmann Method coupled with a 
    molecular dynamics representation of rigid particles and a dipole-based magnetic field model. The system is modelled on a water-2,6-lutidine 
    bijel casting mixture stabilized by micron-sized nickel-coated polystyrene particles.
    We first examine the ability of magnetic fields to influence bijel formation by applying a constant field during spinodal decomposition
    of fluid mixtures containing disc-like, spherical, and rod-like particles. While no significant change in domain size is observed for 
    spherical particles, bijels stabilized by discs and rods show slight increases in domain size and become anisotropic, as measured by 
    tortuosity and directional domain size.
    
    Further analysis reveals that the coarsening rates become direction-specific for ellipsoidal particles, 
    suggesting that jamming occurs anisotropically due to particle alignment with the magnetic field. This alignment, governed by the 
    orientation of the magnetic moment relative to the particle's long axis, also affects how particles arrange themselves at the fluid 
    interface. Particle alignment to the magnetic field affects the curvature of the interface as particles with smaller cross sectional area 
    are less disruptive to the hyperbolic interface shape. Topological examinations of the morphology, 
    demonstrating that the number of interconnected channels in the system decreased over time and that the average channel sizes obtained follow
    the same trend as that of the domain size. These results highlight how particle shape and magnetic field interactions can be leveraged to 
    guide bijel formation in a directional and controllable manner.
    
    Next, we examine the ability of bijels to undergo microstructure modification post formation.
    This has implications for applications like crossflow reactors and filtration systems, where reversible control over 
    permeability and flow resistance is desirable. By incrementally increasing and decreasing the magnetic field on a bijel stabilized with 
    rod-like particles, we observe that the microstructure can be modified post-synthesis. Domain size increases nonlinearly with 
    applied field strength and remains altered even after the field is reduced, indicating that the structure remains in a kinetically arrested
    state.To probe this further, we evaluate field-driven coarsening in bijels stabilized with rod and disc-like particles. Upon field application, 
    particles reorient, leading to anisotropic domains similar to those formed during synthesis under a field. The temporal evolution of 
    microstructure involves increased particle ordering, interface alignment, and rearrangement, demonstrating a complex interplay of factors. 
    Notably, the extent of domain size change is negatively correlated with the initial ordering of particles.
    
    Given that many magnetically responsive materials exhibit field-dependent rheological behavior (e.g., shear thickening in ferrofluids), 
    we investigate whether bijels exhibit similar effects. Prior studies have shown that shear can induce domain coarsening and particle 
    ejection in bijels. Additionally, emulsions stabilized by ellipsoidal particles exhibit reduced viscosity with increased particle ordering because 
    aligned particles create less resistance to flow. In this work, we explore how magnetic fields and initial microstructure affect the shear 
    response of bijels stabilized by ellipsoidal particles. As particle ordering increases, the viscosity and shear-thinning behavior decrease for 
    bijels stabilized by disc- and rod-like particles. We also characterize that the yield stress is dependent upon the friction between particles
    that is a function of the arrangement of particles on the interface, affected by the application of magnetic fields. These results suggest 
    that magnetic field-driven particle ordering can be used to tailor the rheological behavior of bijels, offering a strategy to reduce viscosity 
    and modulate shear-thinning by controlling interfacial microstructure. 
    
    In conclusion, this dissertation demonstrates that magnetic fields offer a viable and tunable method for controlling bijel microstructures 
    both during and after synthesis, and it characterizes the constant shear response of magnetically responsive bijels. These findings 
    lay the groundwork for developing adaptive, magnetically responsive bijels suitable for porous material templates or as a soft matter 
    system for use in drug release or bioengineering applications.

\end{front}